Automatically drawing vegetation maps using digital time-lapse cameras in alpine ecosystems

### 2022-06-29 paper/paper.Rmd
georectification accuracy added

The effects of climate change on terrestrial ecosystems are particularly significant in alpine regions (\cite{IPCC2007}). Alpine vegetation depends on severe conditions such as low temperatures and long snow-covered periods. Thus alpine areas have rare and unique species adapted to the extreme environments. Several studies have reported that recent global climatic changes, e.g., increasing temperatures and reducing snow-covered periods, have accelerated the invasion of non-native species into alpine areas (see \cite{Alexander2016AlpBotany}). In Japan, dwarf bamboo (*Sasa kurilensis*) has invaded alpine snow meadows, probably driven by the extension of the snow-free period (\cite{Kudo2011EcoEvo}). Also, climate change has affected the growth and phenologies of native species. For example, the growth of dwarf pine (*Pinus pumila*), a dominant species in Japanese alpine regions, has been affected by climatic conditions such as temperature and snowmelt (\cite{Amagai2015EcoRes}). Monitoring and predicting such changes are essential for effective conservation planning. Since the impact of climate change on alpine vegetation varies depending on species and the microhabitats (\cite{Kudo2010AAA}), spatially high-resolution monitoring with a wide range is required.

@@

On the other hand, researchers have also utilized automated digital time-lapse cameras mounted on the ground for monitoring green-leaf phenologies in forests (\cite{Richardson2009EcolAppl}), grasslands (\cite{Browning2017RemSen}), and alpine meadows (\cite{IdeOguma2013EcolInfom}). Unlike satellite imagery, such cameras provide images free of clouds and atmospheric effects. Also, they can obtain high-resolution (i.e., sub-meter scale) and frequent (i.e., daily or hourly) images at a meager cost. These studies set some regions of interest (ROI) in the images and calculate the phenology index (e.g., excess greenness, \cite{Woebbecke1995ASAE}). Also, we can visually interpret the vegetation distribution and its changes from such time-lapse images. However, few studies have tackled this. This lack of studies seems to be because applying such repeat photography in monitoring vegetation distribution has two technical challenges.

First, unlike satellites' multispectral sensors, ordinal digital cameras can only obtain three bands (Red, Green, and Blue), making it harder to classify the vegetation. Second, since digital time-lapse cameras are mounted on the ground, transforming these images into geospatial data (e.g., orthoimage) is challenging. In other words, even if we find a vegetation change, we cannot quantitatively measure and analyze it as geographic data. It is essential to treat ground-based images as geographic data to utilize them in conservation planning.

This study proposes an automated method for drawing vegetation maps and locating and measuring vegetation changes with a digital time-lapse camera by solving these two challenges. We solved the first challenge by utilizing temporal changes in leaf colors in vegetation classification. We also developed an accurate method for transforming a ground-based photograph into geographic data to tackle the second challenge. Finally, we show an example application of our method by detecting and localizing vegetation changes with an 8-years digital time-lapse imagery of the Japanese alps. We aim to use cheap but powerful digital time-lapse cameras in alpine ecosystem conservation.

@@

We used repeat photography data owned by National Institute for Environmental Studies, Japan (NIES). All the images are publically available on NIES' webpage (<https://db.cger.nies.go.jp/gem/ja/mountain/station.html?id=2>). In 2010, NIES installed the digital time-lapse camera (EOS 5D MK2, Canon Inc., 21 M pixels) on a mountain lodge Murodo-sanso (about 2350 m a.s.l., above the forest limit), located at the foot of Mt. Tateyama (3015 m a.s.l.), in the Nothern Japanese Alps. The camera takes one photograph per hour, from 6 a.m. to 7 p.m. . The camera's field of view (FOV) includes Mt. Tateyama, which ranges from about 2350 m a.s.l. to 3015 m a.s.l. in elevation. The area has a complex mosaic-like vegetation structure because of its topography, including rocks, cliffs, curls, and moraines. From April to November, the camera has observed the snowmelt and seasonal phenology of evergreen, deciduous dwarf trees (e.g., *Pinus pumila*, *Sorbus* sp.), dwarf bamboos (e.g., *Sasa kurilensis*), and alpine herbaceous plants (e.g., *Geum pentapetalum*, *Nephrophyllidium crista-galli*). We used the images from late summer to late fall of 2012 and 2020 to observe the distribution changes of the dwarf pine (*Pinus pumila*): the dominant species in Japanese alps, and the invasive dwarf bamboo (*Sasa kurilensis*).

@@

First, we selected images that are suitable for vegetation classification. We choose four days with good weather from late summer to late fall each year (9/19, 10/1, 10/11, 10/23 in 2010. 9/19, 10/2, 10/11, 10/23 in 2020). We used the images of this season because we can classify vegetation with the patterns of autumn foliage coloration. Also, we chose four images from 11 a.m. to 2 p.m. each day to avoid the effect of temporal noise such as shadows. Finally, we got 16 images for each year.

@@

Since images are slightly misaligned with each other due to the effect of wind and human interactions, we aligned them before processing. We implemented the program with Python3 programming language and OpenCV4 (<https://opencv.org/>) image processing library. First, we set one image of 2012 as the alignment target. Next, we automatically found matching keypoints between the target and other images using AKAZE local feature extractor (\cite{Alcantarilla2013AKAZE}) and K-nearest neighbor matcher. Then, we searched and applied the homography matrix that minimizes the distance between each pair of the matching points, using OpenCV's "findHomography" function. Because not all matched points are correct, we estimated the homography matrix using the RANdom SAmple Consensus (RANSAC) to avoid influences of such outliers.

@@

Next, we classified the pixel time series of repeat photography imagery into vegetation. Because deciduous plants have great differences in autumn phenology among species, researchers have used that information for vegetation classification with satellite imagery (e.g., \cite{Tigges2013RemSenEnv}, \cite{Son2013RemSen}, \cite{Heupel2018PFG}). In our target area, we can recognize the vegetation type with the pixel time series of autumn (Fig. 2). However, no research has applied this technique to ground-based repeat photography imagery. We developed a deep-learning method to take advantage of high-resolution and frequent repeat photography data. Fig.3 shows the classification process.

@@

Since ground-based photographs can provide high spatial resolution (sub-meter scale in our dataset), we can use leaf texture as additional information for classification. For example, we can see a glossy surface on dwarf bamboos and a mat surface on dwarf pines. Thus, we used a small patch (9x9 pixels square) rather than a single pixel as an input of the model. Therefore, a model input is a time series of image patches.

Our model has two components to deal with this data structure (see Fig. 3). First, we extracted each patch's features (e.g., texture) using Convolutional Neural Network (CNN) layers (Fig. 4a). CNN is a neural network specialized in recognizing spatial structures of data, such as images. The CNN part outputs a time series of extracted features. Second, we used Recurrent Neural Net (RNN) layers (Fig. 4b) to classify the temporal patterns of the features extracted by the CNN part. RNN is a neural network specialized in recognizing temporal or sequential data dynamics, such as text and speech. Amongst many variants of RNN, we used Long Short Time Memory (LSTM, \cite{Hochreiter1997LSTM}). Combining CNN and RNN, our model can classify the input image-patch time series considering the colors and textures of each patch and their temporal patterns. This CNN-RNN architecture has also been used for audio classification(\cite{Shi2015CRNNtext}) and scene text recognition(\cite{Shi2015CRNNtext}).

Using a Deep Learning method has another positive side effect; mini-batch training. Since we used high-resolution images (16 x 21M pix), the training dataset became so immense that we could not feed them to the model at once: that consumes the computer's RAM too much. However, using Deep Learning methods enables us to provide them in small portions (called mini-batches) to save RAM consumption.

@@

We set 5 vegetation classes: dwarf pine, dwarf bamboo, other vegetation, no vegetation, and sky. Using a free image annotation software (Semantic Segmentation Editor, Hitachi, <https://github.com/Hitachi-Automotive-And-Industry-Lab/semantic-segmentation-editor>), an expert drew polygons on an image of 2015 for each class. Since vegetation might be different in 2012, 2015, and 2020, applying this teacher data to the image of 2012 and 2020 may cause misclassification. However, vegetation changes are expected to occur at the edge of the plant community. Thus we shrink each polygon with several pixels before applying it to the training.

@@

We implemented the classifier with Python3 language and PyTorch deep neural network library (<https://pytorch.org/>). All source codes are publically available via GitHub (<https://github.com/0kam/xxxx>).

@@

```{r, echo=FALSE, message=FALSE, fig.cap="Cross Validation Results"}
df <- read_csv("../runs/cnn_lstm9x9_cv_5_ep_200/staritfied_cv.csv",
               col_select = c(metrics, vegetation, value, fold))
theme_gtsummary_mean_sd()

@@

```{r, vegetation, echo=FALSE, message=FALSE, fig.cap="Vegetation classification results", out.width="100%", auto_pdf = TRUE}
knitr::include_graphics("vegetation.jpg")
```

>>>>

The effects of climate change on terrestrial ecosystems are particularly significant in alpine regions (\cite{IPCC2007}). Alpine vegetation depends on severe conditions such as low temperatures and long snow-covered periods. Thus alpine areas have rare and unique species adapted to the extreme environments. Several studies have reported that recent global climatic changes, e.g., increasing temperatures and reducing snow-covered periods, have accelerated the invasion of non-native species into alpine areas (see \cite{Alexander2016AlpBotany}). In Japan, dwarf bamboo (*Sasa kurilensis*) has invaded alpine snow meadows, probably driven by the extension of the snow-free period (\cite{Kudo2011EcoEvo}). Also, climate change has affected the growth and phenologies of native species. For example, the growth of dwarf pine (*Pinus pumila*), a dominant species in Japanese alpine regions, has been affected by climatic conditions such as temperature and snowmelt (\cite{Amagai2015EcoRes}). Effective conservation planning requires early detection and constant monitoring of such vegetation changes. Also, since the impact of climate change on alpine vegetation varies depending on species and the microhabitats (\cite{Kudo2010AAA}), spatially high-resolution monitoring with a wide range is required.

@@

On the other hand, researchers have also utilized automated digital time-lapse cameras mounted on the ground for monitoring green-leaf phenologies in forests (\cite{Richardson2009EcolAppl}), grasslands (\cite{Browning2017RemSen}), and alpine meadows (\cite{IdeOguma2013EcolInfom}). Unlike satellite imagery, such cameras provide images free of clouds and atmospheric effects. Also, they can obtain high-resolution (i.e., sub-meter scale) and frequent (i.e., daily or hourly) images at a meager cost. These studies set some regions of interest (ROI) in the images and calculate the phenology index (e.g., excess greenness, \cite{Woebbecke1995ASAE}). However, few studies have utilized such images in monitoring vegetation distributions. This lack of studies seems to be because applying such repeat photography in monitoring vegetation distribution has two technical challenges.

First, unlike satellites' multispectral sensors, ordinal digital cameras can only obtain three bands (Red, Green, and Blue), making it harder to classify the vegetation. Second, since digital time-lapse cameras are mounted on the ground, transforming these images into geospatial data (e.g., orthoimage) is challenging. In other words, even if we classify the vegetation from such images, we cannot quantitatively measure and analyze it as geographic data. It is essential to treat ground-based images as geographic data to utilize them in conservation planning.

This study proposes an automated method for drawing vegetation maps with a digital time-lapse camera by solving these two challenges. We solved the first challenge by using time-lapse images to classify vegetation. Since the autumn leaf phenology varies among species, we utilized that information. We show the effectiveness of such phenological information in vegetation classification. We also developed a novel method for transforming a ground-based photograph into geographic data to tackle the second challenge. Finally, we show an example of a vegetation map drawn by the proposed method. We aim to use cheap but powerful digital time-lapse cameras in alpine ecosystem monitoring and conservation.

@@

We used repeat photography data owned by National Institute for Environmental Studies, Japan (NIES). All the images are publically available on NIES' webpage (https://db.cger.nies.go.jp/gem/ja/mountain/station.html?id=2). In 2010, NIES installed the digital time-lapse camera (EOS 5D MK2, Canon Inc., 21 M pixels) on a mountain lodge Murodo-sanso (about 2350 m a.s.l., above the forest limit), located at the foot of Mt. Tateyama (3015 m a.s.l.), in the Nothern Japanese Alps. The camera takes a photograph per hour, from 6 a.m. to 7 p.m. . The camera's field of view (FOV) includes Mt. Tateyama, which ranges from about 2350 m a.s.l. to 3015 m a.s.l. in elevation. The area has a complex mosaic-like vegetation structure because of its topography, including rocks, cliffs, curls, and moraines. From April to November, the camera has observed the snowmelt and seasonal phenology of evergreen(e.g., *Pinus pumila*) and deciduous (*Sorbus* sp.,  *Betula ermanii*) dwarf trees, dwarf bamboos (e.g., *Sasa kurilensis*), and alpine shrubs and herbaceous plants (e.g., *Geum pentapetalum*, *Nephrophyllidium crista-galli*). This study used images from the summer and fall of 2015 to classify vegetation with the temporal patterns of the leaf color.

@@

First, we selected images that are suitable for vegetation classification. We choose seven days with good weather from late summer to late fall of 2015 (8/25, 9/5, 9/12, 9/20, 9/26, 10/3, 10/10). We used the images of this season because we can separate vegetation from the patterns of autumn foliage coloration.

@@

Since images are slightly misaligned, we aligned them before processing. We implemented the program with the Python3 programming language and OpenCV4 (https://opencv.org/) image processing library. First, we set one image of 2015 as the alignment target. Next, we automatically found matching keypoints between the target and other images using the AKAZE local feature extractor (\cite{Alcantarilla2013AKAZE}) and K-nearest neighbor matcher. Then, we searched and applied the homography matrix that minimizes the distance between each pair of the matching points, using OpenCV's "findHomography" function. Applying the estimated homography matrix, we could align the images accurately (0.654 pixels in root mean square error of the matching points). Finally, we prepared an input mask to define image regions that should be ignored in the following procedure, such as the sky and the regions too close to the camera.

@@

Since we successfully aligned the images, we can stack the images and extract a time series of pixel values (Red, Green, and Blue, Fig. 1) for each pixel. Such pixel time series reflects the temporal patterns of leaf colors. Because deciduous plants have great differences in autumn phenology among species, researchers have used that information for vegetation classification with satellite imagery (e.g., \cite{Tigges2013RemSenEnv}, \cite{Son2013RemSen}, \cite{Heupel2018PFG}). However, no research has applied this technique to ground-based repeat photography imagery. We implemented Support Vector Machine (SVM) and Recurrent Neural Network (RNN) based vegetation classification methods in this study. We tested the effects of using pixel time series on the classification performance.

@@

We prepared two supervised models, SVM and RNN, to classify the pixel time series into vegetation categories. SVM is one of the most popular machine learning models in remote sensing and has many applications (\cite{Mountrakis2011SVMReview}), including vegetation classification with multitemporal satellite imagery (\cite{Tigges2013RemSenEnv}). RNN is a neural network that recognizes temporal or sequential data dynamics. Researchers have also utilized RNN for remote sensing tasks, such as land cover classification, with multi-temporal satellite imagery (\cite{Ienco2017RemSenLSTM}, \cite{Sharma2018NN}). Amongst many variants of RNN, we used Long Short Time Memory (LSTM, \cite{Hochreiter1997LSTM}), one of the most well-known RNN architectures. We also classified the pixel of every single image separately using SVM classifiers to test whether using multi-temporal imagery increases the classification performance.

@@

We set 7 vegetation classes: Dwarf Pine (*Pinus pumila*), Dwarf Bamboo (*Sasa kurilensis*), Rowans (*Sorbus sambucifolia*, *Sorbus matsumurana*), Birch (*Betula ermanii*), Alder (*Alnus viridis* subsp. *maximowiczii*), Other Vegetations (such as alpine shrubs and herbaceous plants), and No Vegetation. Using an open-source image annotation software (Semantic Segmentation Editor, Hitachi, https://github.com/Hitachi-Automotive-And-Industry-Lab/semantic-segmentation-editor), an expert prepared a teacher dataset for each class. Then we validated the teacher dataset with a set of telephotos taken in the summer and fall of 2016.

@@

We implemented the classifier with Python3 language, ThunderSVM library (<https://github.com/Xtra-Computing/thundersvm>) for the SVM classifier, and  PyTorch deep neural network library (<https://pytorch.org/>) for the RNN classifier. All source codes are publically available via GitHub (<https://github.com/0kam/xxxx>).

@@

```#{r, echo=FALSE, message=FALSE, fig.cap="Cross Validation Results"}
df <- read_csv("../runs/cnn_lstm9x9_cv_5_ep_200/staritfied_cv.csv",
               col_select = c(metrics, vegetation, value, fold))
theme_gtsummary_mean_sd()

@@

```#{r, vegetation, echo=FALSE, message=FALSE, fig.cap="Vegetation classification results", out.width="100%", auto_pdf = TRUE}
knitr::include_graphics("vegetation.jpg")
```

### 2022-06-29 paper/paper.tex
georectification accuracy added

The effects of climate change on terrestrial ecosystems are particularly significant in alpine regions (\cite{IPCC2007}). Alpine vegetation depends on severe conditions such as low temperatures and long snow-covered periods. Thus alpine areas have rare and unique species adapted to the extreme environments. Several studies have reported that recent global climatic changes, e.g., increasing temperatures and reducing snow-covered periods, have accelerated the invasion of non-native species into alpine areas (see \cite{Alexander2016AlpBotany}). In Japan, dwarf bamboo (\emph{Sasa kurilensis}) has invaded alpine snow meadows, probably driven by the extension of the snow-free period (\cite{Kudo2011EcoEvo}). Also, climate change has affected the growth and phenologies of native species. For example, the growth of dwarf pine (\emph{Pinus pumila}), a dominant species in Japanese alpine regions, has been affected by climatic conditions such as temperature and snowmelt (\cite{Amagai2015EcoRes}). Monitoring and predicting such changes are essential for effective conservation planning. Since the impact of climate change on alpine vegetation varies depending on species and the microhabitats (\cite{Kudo2010AAA}), spatially high-resolution monitoring with a wide range is required.

@@

We used repeat photography data owned by National Institute for Environmental Studies, Japan (NIES). All the images are publically available on NIES' webpage (\url{https://db.cger.nies.go.jp/gem/ja/mountain/station.html?id=2}). In 2010, NIES installed the digital time-lapse camera (EOS 5D MK2, Canon Inc., 21 M pixels) on a mountain lodge Murodo-sanso (about 2350 m a.s.l., above the forest limit), located at the foot of Mt. Tateyama (3015 m a.s.l.), in the Nothern Japanese Alps. The camera takes one photograph per hour, from 6 a.m. to 7 p.m. . The camera's field of view (FOV) includes Mt. Tateyama, which ranges from about 2350 m a.s.l. to 3015 m a.s.l. in elevation. The area has a complex mosaic-like vegetation structure because of its topography, including rocks, cliffs, curls, and moraines. From April to November, the camera has observed the snowmelt and seasonal phenology of evergreen, deciduous dwarf trees (e.g., \emph{Pinus pumila}, \emph{Sorbus} sp.), dwarf bamboos (e.g., \emph{Sasa kurilensis}), and alpine herbaceous plants (e.g., \emph{Geum pentapetalum}, \emph{Nephrophyllidium crista-galli}). We used the images from late summer to late fall of 2012 and 2020 to observe the distribution changes of the dwarf pine (\emph{Pinus pumila}): the dominant species in Japanese alps, and the invasive dwarf bamboo (\emph{Sasa kurilensis}).

@@

Since images are slightly misaligned with each other due to the effect of wind and human interactions, we aligned them before processing. We implemented the program with Python3 programming language and OpenCV4 (\url{https://opencv.org/}) image processing library. First, we set one image of 2012 as the alignment target. Next, we automatically found matching keypoints between the target and other images using AKAZE local feature extractor (\cite{Alcantarilla2013AKAZE}) and K-nearest neighbor matcher. Then, we searched and applied the homography matrix that minimizes the distance between each pair of the matching points, using OpenCV's ``findHomography'' function. Because not all matched points are correct, we estimated the homography matrix using the RANdom SAmple Consensus (RANSAC) to avoid influences of such outliers.

@@

Then we transform the distorted camera coordinates to the image coordinates by perspective projection. During the perspective projection, a closer object is drawn larger. We used a \(4 \times 4\) projection matrix \(M_{proj}\) (\ref{proj_mat}), that represents the camera's horizontal (\(fov_x\)) and vertical (\(fov_z\)) FoV. Finally, we can get the location of each point of the DSM on the image as \(X_{image}, Z_{image}\) (\ref{proj_tf}) i.e., we can generate a virtual image with given set of camera parameters.

@@

\begin{verbatim}
## Warning: One or more parsing issues, see `problems()` for details
\end{verbatim}

\begin{table}

\caption{\label{tab:unnamed-chunk-1}Cross validation result \label{tab:vegetation_cv}}
\centering
\begin{tabular}[t]{llll}
\toprule
vegetation & f1-score & precision & recall\\
\midrule
 & 0.986 & 0.984 & 0.988\\
\cmidrule{2-4}
\multirow{-2}{*}{\raggedright\arraybackslash Macro Average} & (0.006) & (0.010) & (0.001)\\
\cmidrule{1-4}
 & 0.997 & 0.997 & 0.997\\
\cmidrule{2-4}
\multirow{-2}{*}{\raggedright\arraybackslash Weighted Average} & (0.001) & (0.001) & (0.001)\\
\cmidrule{1-4}
 & 0.987 & 0.980 & 0.994\\
\cmidrule{2-4}
\multirow{-2}{*}{\raggedright\arraybackslash Dwarf Pine} & (0.004) & (0.010) & (0.003)\\
\cmidrule{1-4}
 & 0.962 & 0.964 & 0.961\\
\cmidrule{2-4}
\multirow{-2}{*}{\raggedright\arraybackslash Dwarf Bamboo} & (0.010) & (0.020) & (0.004)\\
\cmidrule{1-4}
 & 0.998 & 0.999 & 0.997\\
\cmidrule{2-4}
\multirow{-2}{*}{\raggedright\arraybackslash Other vegetation} & (0.001) & (0.000) & (0.002)\\
\cmidrule{1-4}
 & 0.978 & 0.972 & 0.985\\
\cmidrule{2-4}
\multirow{-2}{*}{\raggedright\arraybackslash Non Vegetation} & (0.028) & (0.053) & (0.004)\\
\cmidrule{1-4}
 & 1.000 & 1.000 & 1.000\\
\cmidrule{2-4}
\multirow{-2}{*}{\raggedright\arraybackslash Sky} & (0.000) & (0.000) & (0.000)\\
\bottomrule
\multicolumn{4}{l}{\rule{0pt}{1em}\textit{Note: }}\\
\multicolumn{4}{l}{\rule{0pt}{1em}Mean (SD) of 5-Fold Cross-Varidation}\\
\end{tabular}
\end{table}

\begin{figure}
\includegraphics[width=1\linewidth]{vegetation} \caption{Vegetation classification results}\label{fig:vegetation}
\end{figure}

>>>>

The effects of climate change on terrestrial ecosystems are particularly significant in alpine regions (\cite{IPCC2007}). Alpine vegetation depends on severe conditions such as low temperatures and long snow-covered periods. Thus alpine areas have rare and unique species adapted to the extreme environments. Several studies have reported that recent global climatic changes, e.g., increasing temperatures and reducing snow-covered periods, have accelerated the invasion of non-native species into alpine areas (see \cite{Alexander2016AlpBotany}). In Japan, dwarf bamboo (\emph{Sasa kurilensis}) has invaded alpine snow meadows, probably driven by the extension of the snow-free period (\cite{Kudo2011EcoEvo}). Also, climate change has affected the growth and phenologies of native species. For example, the growth of dwarf pine (\emph{Pinus pumila}), a dominant species in Japanese alpine regions, has been affected by climatic conditions such as temperature and snowmelt (\cite{Amagai2015EcoRes}). Effective conservation planning requires early detection and constant monitoring of such vegetation changes. Also, since the impact of climate change on alpine vegetation varies depending on species and the microhabitats (\cite{Kudo2010AAA}), spatially high-resolution monitoring with a wide range is required.

@@

We used repeat photography data owned by National Institute for Environmental Studies, Japan (NIES). All the images are publically available on NIES' webpage (\url{https://db.cger.nies.go.jp/gem/ja/mountain/station.html?id=2}). In 2010, NIES installed the digital time-lapse camera (EOS 5D MK2, Canon Inc., 21 M pixels) on a mountain lodge Murodo-sanso (about 2350 m a.s.l., above the forest limit), located at the foot of Mt. Tateyama (3015 m a.s.l.), in the Nothern Japanese Alps. The camera takes a photograph per hour, from 6 a.m. to 7 p.m. . The camera's field of view (FOV) includes Mt. Tateyama, which ranges from about 2350 m a.s.l. to 3015 m a.s.l. in elevation. The area has a complex mosaic-like vegetation structure because of its topography, including rocks, cliffs, curls, and moraines. From April to November, the camera has observed the snowmelt and seasonal phenology of evergreen(e.g., \emph{Pinus pumila}) and deciduous (\emph{Sorbus} sp., \emph{Betula ermanii}) dwarf trees, dwarf bamboos (e.g., \emph{Sasa kurilensis}), and alpine shrubs and herbaceous plants (e.g., \emph{Geum pentapetalum}, \emph{Nephrophyllidium crista-galli}). This study used images from the summer and fall of 2015 to classify vegetation with the temporal patterns of the leaf color.

@@

Since images are slightly misaligned, we aligned them before processing. We implemented the program with the Python3 programming language and OpenCV4 (\url{https://opencv.org/}) image processing library. First, we set one image of 2015 as the alignment target. Next, we automatically found matching keypoints between the target and other images using the AKAZE local feature extractor (\cite{Alcantarilla2013AKAZE}) and K-nearest neighbor matcher. Then, we searched and applied the homography matrix that minimizes the distance between each pair of the matching points, using OpenCV's ``findHomography'' function. Applying the estimated homography matrix, we could align the images accurately (0.654 pixels in root mean square error of the matching points). Finally, we prepared an input mask to define image regions that should be ignored in the following procedure, such as the sky and the regions too close to the camera.

@@

Then we transform the distorted camera coordinates to the image coordinates by perspective projection. During the perspective projection, a closer object is drawn larger. We used a \(4 \times 4\) projection matrix \(M_{proj}\) (\ref{proj_mat}), that represents the camera's horizontal (\(fov_x\)) and vertical (\(fov_z\)) FoV. Finally, we can get the image coordinates of each point of the DSM as \(X_{image}, Z_{image}\) (\ref{proj_tf}).

@@

```\#\{r, echo=FALSE, message=FALSE, fig.cap=``Cross Validation Results''\}
df \textless- read\_csv(``../runs/cnn\_lstm9x9\_cv\_5\_ep\_200/staritfied\_cv.csv'',
col\_select = c(metrics, vegetation, value, fold))
theme\_gtsummary\_mean\_sd()

df \%\textgreater\%
filter(metrics != ``support'') \%\textgreater\%
mutate(vegetation = translate\_classes(vegetation)) \%\textgreater\%
mutate(vegetation = factor(vegetation, levels = vegetation\_levels)) \%\textgreater\%
group\_by(., vegetation, metrics) \%\textgreater\%
summarise(
mean = sprintf(``\%1.3f'', mean(value)),
sd = sprintf(``(\%1.3f)'', sd(value))
) \%\textgreater\%
pivot\_longer(cols=c(mean, sd), names\_to=``var'') \%\textgreater\%
pivot\_wider(names\_from=metrics, values\_from=value) \%T\textgreater\%
write\_csv(``table1.csv'') \%\textgreater\%
select(-var) \%\textgreater\%
kable(format=``latex'', booktabs=TRUE, caption = ``Cross validation result \textbackslash label\{tab:vegetation\_cv\}'') \%\textgreater\%
kable\_styling() \%\textgreater\%
collapse\_rows(columns=1) \%\textgreater\%
footnote(general = ``Mean (SD) of 5-Fold Cross-Varidation'')

\begin{verbatim}
```#{r, vegetation, echo=FALSE, message=FALSE, fig.cap="Vegetation classification results", out.width="100%", auto_pdf = TRUE}
knitr::include_graphics("vegetation.jpg")
\end{verbatim}
